How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-18 tse-paper/content.tex
First example of subfigures

\begin{figure}[!t]
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for an increasing training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{figure}

\begin{figure}[!t]
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with KWS for an increasing number of structural categories in the training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{figure}

@@

\begin{figure}[!t]
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
		\caption{Precision, recall and F$_{1}$-score of chunk retrieval when PBE could synthesize a consistent program compared with the size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{figure}

\begin{figure}[!t]
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Results of chunk retrieval with PBE for an increasing number of structural categories in the training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{figure}

>>>>

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Results of chunk retrieval with  (KWS)}
\end{figure*}

@@

\begin{figure*}
\begin{subfigure}[!t]{\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}

\begin{subfigure}[!t]{\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Increasing number of structural categories in the training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{subfigure}

\caption{Results of chunk retrieval with Program Synthesis by Example (PBE)}
\end{figure*}

### 2020-03-18 tse-paper/paper.tex
Add motivation
include loads of text and graphics from thesis, fix graphics, start adapting heading levels
Edit abstract
Add Litsurvey protocol
Prepare figures for inclusion
First example of subfigures

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{How to Analyze Build Logs\\ ---\\ A~Comparative Study of Chunk~Retrieval~Techniques}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc 
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

>>>>

\usepackage{todonotes}
%\setuptodonotes{inline, color=cyan!50}
\usepackage{cleveref}
%\usepackage{subfigure}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mdframed,xcolor}

\newenvironment{figureax}[1][htbp]% Redefine figure
  {\oldfigure[#1]\mdframed[backgroundcolor=blue!15]}
  {\endmdframed\endoldfigure}

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%
%
%\IEEEcompsocitemizethanks is a special \thanks that produces the bulleted
% lists the Computer Society journals use for "first footnote" author
% affiliations. Use \IEEEcompsocthanksitem which works much like \item
% for each affiliation group. When not in compsoc mode,
% \IEEEcompsocitemizethanks becomes like \thanks and
% \IEEEcompsocthanksitem becomes a line break with idention. This
% facilitates dual compilation, although admittedly the differences in the
% desired content of \author between the different types of papers makes a
% one-size-fits-all approach a daunting prospect. For instance, compsoc 
% journal papers have the author affiliations above the "Manuscript
% received ..."  text while in non-compsoc journals this is reversed. Sigh.

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)

\bibliography{paper}
